Tidy data structure to support exploration and modeling of temporal-context data

### 2018-11-05 main.Rmd
replaced nyc flights with national-wide 5 airports

It encourage users to look into the data as earlier as possible, examining the data quality issues.

@@

[Change New York Airports to others to be able to see seasonal effects]

A closer examination of New York airports will give an indication about how well the busiest airports manage the outflow traffic on a daily basis. A subset that contains observations for EWR, JFK and LGA airports is obtained first. The succeeding operations compute delayed percentages every day at each airport, which are framed as grey lines in Figure \@ref(fig:nyc-monthly-plot). LGA fluctuates a lot compared to the other two. What superimposes on these lines is two-month moving averages so that a temporal trend is more visible. The number of days for each month is variable. Moving averages for two months call for computing weighted mean. But this can also be accomplished using a pair of commonly used verbs--`nest()` and `unnest()` to handle list-columns, without worrying weights specification. The sliding with large window size smoothes out the fluctuations and gives a stable trend around 25% over the year.

```{r nyc-flights}
```

```{r nyc-delay}
```

```{r nyc-monthly-1}
```

```{r nyc-monthly-2}
```

```{r nyc-monthly-plot, fig.cap = "(ref:nyc-monthly-plot-cap)"}
```

(ref:nyc-monthly-plot-cap) Daily delayed percentages for departure with two-month moving averages overlaid at New York airports. There are many fluctuations observed at LGA airport. The estimates of temporal trend are around 25% across three airports, highlighting relatively less delay in Fall.

@@

>>>>

It encourage users to look into the data as earlier as possible, assessing the data quality issues.

@@

A closer examination of New York airports will give an indication about how well the busiest airports manage the outflow traffic on a daily basis. A subset that contains observations for EWR, JFK and LGA airports is obtained first. The succeeding operations compute delayed percentages every day at each airport, which are framed as grey lines in Figure \@ref(fig:sel-monthly-plot). LGA fluctuates a lot compared to the other two. What superimposes on these lines is two-month moving averages so that a temporal trend is more visible. The number of days for each month is variable. Moving averages for two months call for computing weighted mean. But this can also be accomplished using a pair of commonly used verbs--`nest()` and `unnest()` to handle list-columns, without worrying weights specification. The sliding with large window size smoothes out the fluctuations and gives a stable trend around 25% over the year.

```{r sel-flights}
```

```{r sel-delay}
```

```{r sel-monthly-1}
```

```{r sel-monthly-2}
```

```{r sel-monthly-plot, fig.cap = "(ref:sel-monthly-plot-cap)", fig.height = 6}
```

(ref:sel-monthly-plot-cap) Daily delayed percentages for departure with two-month moving averages overlaid at five international airports. There are many fluctuations observed at LGA airport. The estimates of temporal trend are around 25% across three airports, highlighting relatively less delay in Fall.

@@

## Smart-Grid Customer Data in Australia

<https://data.gov.au/dataset/smart-grid-smart-city-customer-trial-data>
